Choosing TTC Subway Service Provides the Most Time Stability during Weekday Rush-Hours

### 2024-09-24 outputs/paper/paper.qmd
fixed position of tables and re-rendered

Where the data comes from - All data used for and throughout the paper are extracted from Open Data Toronto Portal [@OpenDataToronto]. TTC Bus Delay data [@Bus], TTC Streetcar Delay [@Streetcar], TTC Subway Delay [@Subway] and TTC Subway Delay Codes [@Subway] are retrieved to compare the delay magnitudes of different services. Data is cleaned and analyzed using the open source statistical programming language R [@citeR] and supporting packages tidyverse [@tidyverse], janitor [@janitor], dplyr [@dplyr], hms [@hms], ggplot2 [@ggplot2], patchwork [@patchwork], kableExtra [@kableExtra], and knitr [@knitr].
\
\
For all delay dataset, only data in 2023 were chosen. There are three
main reasons for this choice:

**1.** 2023 data is the most recent full-year data and offers the best reference for current (2024) delay patterns.

**2.** COVID-19 impacted TTC operating capacity and styles in other years close to 2024.

**3.** data from earlier years (before 2020) were structured very differently.

@@

```{r}
#| label: tbl-reason
#| tbl-cap: Top 5 Most Popular Reason for Delay
#| fig-pos: "H"
#| echo: false
#| message: false

@@

knitr::kable(reason_delay, col.names = c("Bus", "Streetcar", "Subway"), align = c("c", "c", "c")) |>
  kableExtra::kable_styling(position = "center")
```

@@

```{r}
#| label: tbl-lines
#| tbl-cap: Most delayed Lines for each TTC Service
#| fig-pos: "H"
#| echo: false
#| message: false

>>>>

Where the data comes from - All data used for and throughout the paper are extracted from Open Data Toronto Portal [@OpenDataToronto]. TTC Bus Delay data [@Bus], TTC Streetcar Delay [@Streetcar], TTC Subway Delay [@Subway] and TTC Subway Delay Codes [@Subway] are retrieved to compare the delay magnitudes of different services. Data is cleaned and analyzed using the open source statistical programming language R [@citeR] and supporting packages tidyverse [@tidyverse], janitor [@janitor], dplyr [@dplyr], hms [@hms], ggplot2 [@ggplot2], patchwork [@patchwork], kableExtra [@kableExtra], and knitr [@knitr].

For all delay dataset, only data in 2023 were chosen. There are three
main reasons for this choice:

>**1.** 2023 data is the most recent full-year data and offers the best reference for current (2024) delay patterns.

>**2.** COVID-19 impacted TTC operating capacity and styles in other years close to 2024.

>**3.** data from earlier years (before 2020) were structured very differently.

@@

```{r}
#| label: tbl-reason
#| tbl-cap: Top 5 Most Popular Reason for Delay
#| table.position: "H"
#| echo: false
#| message: false

@@

knitr::kable(reason_delay, col.names = c("Bus", "Streetcar", "Subway"), align = c("c", "c", "c")) |>
  kableExtra::kable_styling(position = "center", font_size = 10)
```

@@

```{r}
#| label: tbl-lines
#| tbl-cap: Most delayed Lines for each TTC Service
#| table.position: "H"
#| echo: false
#| message: false
